---
title: "Lab 05"
author: "Linzhuo Li"
format: html
---

## Data description 
<!--
the nature of the data
the source of the data
the acquisition strategy that will be used
the format of the data
the license of the data
-->

The data that I'm downloading is the
This corpus is a set of 

The data is in an archieved file on the 
[Here]()
in this case, I'm going to 



```{r}
#| label: setup-packages
#| message: false


# load package
library(dplyr)
library(fs)
```


```{r}
file_url <-"https://catalog.ldc.upenn.edu/docs/LDC97S62/swb1_dialogact_annot.tar.gz"
dest_file <- "../data/original/swda.tar.gz"

download.file(url=file_url, destfile = dest_file)
```

Now the file is at 
Since it is archived file, I will need to unarchive it. It's extension is . So I will use the

```{r}
#| label: unarchive-test

# untar(tarfile = "../data/original/swda.tar.gz, exdir")

untar(tarfile = "../data/original/swda.tar.gz", exdir = "../data/original/swda")
```


>--
## Assessing my progress
I learned how to investigate data sources.
I did not found anything chanllenges in this lab as long as I follow it step by step.
{r} 

I consulted [click here](https://qtalr.github.io/qtalrkit/articles/recipe-5.html)
I would like to learn more about how to analyze data through rstudio to show all aspectes of it.


